On The Impact of Atoms of Confusion in JavaScript Code

### 2021-01-28 4_Result.tex
fix the odds ratio report

We first use the \emph{Pearson's Chi-squared test}
to investigate if there is a statistically significant difference
in the frequency of correct and incorrect answers---due to the versions
of the code snippets (confuse and clean code). The result shows that the confusing version of the code snippets impacts code understanding (p-value $< 0.05$). We also use the \emph{Binomial Generalized Logistic Regression} analysis to investigate if either participant
\emph{education} or participant \emph{experience} impact on correctness. Although the results suggest that experience impact correctness, the education level does not. We then replicate the \emph{Pearson's Chi-squared test} for each experience group (see Figure~\ref{fig:xp}) and found that the statistic difference is less significant for those developers with more than ten years of experience.
Finally, we measure the effect size of the clean version of the code snippets into the answers' correctness, using the \emph{Odds Ratio} (OR)
method (see Table~\ref{tab:difference-correctness}). We found a negligible effect size for the atom candidates Arithmetic as Logic, Logic as Control Flow, and Pre Increment. Nonetheless, for the remaining candidates, the effect size is considerable. For instance, the Comma Operators leads to an \emph{Odds Ratio} of
\num{19.02}, meaning that the participants are \num{19.02} times
more likely to correctly interpret the clean version of a code in comparison with the corresponding, confuse version of the code snippet.

>>>>

We first use the \emph{Pearson's Chi-squared test}
to investigate if there is a statistically significant difference
in the frequency of correct and incorrect answers---due to the versions
of the code snippets (confuse and clean code). The result shows that the confusing version of the code snippets impacts code understanding (p-value $< 0.05$). We also use the \emph{Binomial Generalized Logistic Regression} analysis to investigate if either participant
\emph{education} or participant \emph{experience} impact on correctness. Although the results suggest that experience impact correctness, the education level does not. We then replicate the \emph{Pearson's Chi-squared test} for each experience group (see Figure~\ref{fig:xp}) and found that the statistic difference is less significant for those developers with more than ten years of experience.
Finally, we measure the effect size of the clean version of the code snippets into the answers' correctness, using the \emph{Odds Ratio} (OR)
method (see Table~\ref{tab:difference-correctness}). We found a negligible effect size for the atom candidates Arithmetic as Logic, Logic as Control Flow, and Pre Increment. Nonetheless, for the remaining candidates, the effect size is considerable. For instance, the Comma Operators leads to an \emph{Odds Ratio} of
\num{19.02}, meaning that the the odds of a correct answer are \num{19.02} times
higher when interpreting the clean version of a code---in comparison with the corresponding, confuse version of the code snippet.
